\thetitle

### 2021-05-20 writing/mutate-benchmarks.tex
move Louisiana footnote so that the intro to the benchmark section makes sense

\citet{gtnffvf-jfp-2019}'s collection of Typed Racket programs for
systematically measuring the implementation's performance satisfies these
criteria. The benchmark suite consists of fully typed, correct programs, written
by a number of different authors, who have maintained and evolved these programs
over several years. The programs range widely in size, complexity, purpose,
origin and in programming style. The latter is mostly a reference to their
reliance on many Typed Racket features: occurrence typing~\citep{tf-icfp-2010},
types for mutable and immutable data structures~\citep{hpst-sfp-2010}, types for
first-class classes and objects~\citep{tsdtf-oopsla-2012}, and types for
Racket's numeric tower~\citep{stathff-padl-12}.  Finally, all of the programs
are deterministic, so any changes in the programs' behavior between runs can be
solely attributed to the actions of the rational programmer.

>>>>

\citet{gtnffvf-jfp-2019}'s collection of Typed Racket programs for
systematically measuring the implementation's performance satisfies these
criteria. The benchmark suite consists of fully typed, correct programs, written
by a number of different authors, who have maintained and evolved these programs
over several years. The programs range widely in size, complexity, purpose,
origin and in programming style. They rely on many Typed Racket features:
occurrence typing~\citep{tf-icfp-2010}, types for mutable and immutable data
structures~\citep{hpst-sfp-2010}, types for first-class classes and
objects~\citep{tsdtf-oopsla-2012}, and types for Racket's numeric
tower~\citep{stathff-padl-12}.  Finally, all of the programs are deterministic,
so any changes in the programs' behavior between runs can be solely attributed
to the actions of the rational programmer.
